### 2015-04-20 paper.tex
Add acknowledgements from test plan report

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et
malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac
quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam
rhoncus vitae.

>>>>

\section*{Acknowledgments}

This study was supported by the Department of Energy (DOE), Office of Energy
Efficiency and Renewable Energy (EERE), Wind and Water Power Technologies Office
(WWPTO). Sandia National Laboratories is a multi-program laboratory managed and
operated by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.
